Linear stability analysis for \textit{monami} in a submerged sea grass bed

### 2015-10-28 JFM_Revision/grass.tex
Revisions sent to JFM

\newcommand{\ReyNdg}{{\Rey\Ndg}}
\newcommand{\revise}[1]{{\color{blue} {#1}}}

@@

\section{Results - unstable modes and critical parameters}
A threshold in $\Rey$, above which the flow is unstable (Re$(\sigma)>0$) for at least one $k$, emerges from the solution of ~\eqref{Orr-somerfield}. 
The dependence of this threshold $\Rey$, and the corresponding marginally stable wavenumber $k$, on $\delta/H$ and $\hg/H$ is shown in Fig.~\ref{Re_vs_delta}, and is found to compare well with experimental observations of \cite{Ghisal02}.
The threshold $\Rey$ increases with the vegetation density, indicating a competition between the destabilizing shear in the flow, and the stabilizing effect of damping due to vegetation drag.
% A similar conclusion was presented for an analogous problem (flow around an emergent (i.e., $\hg>2H$) sea grass patch), but by assuming $U(y)$ to be a tanh-profile, and neglecting the viscous term \citep{White07}.
%Previous calculations for terrestrial grass either exclude the vegetation drag in their models \cite{Raupach96}, or assume the mean velocity profile \textit{ad hoc} \citep{Raupach96,Delangre06}.
%A threshold flow condition is not reported previously either for terrestrial or submerged marine meadows.
The frequency (Im$(\sigma)$) of the fastest growing mode also agrees well with observed behaviour -- frequency of \monami, maxima in the velocity spectra, and frequency of vortex passage in lab scale experiments \citep{Ghisal02} -- for cases where the vegetation was sufficiently dense to be modeled by a continuum drag field as shown in Fig.~\ref{frequency_comparison}.
\revise{ The measured values of eddy viscosity vary with depth in the water column \citep{Nepf04}; we use $\mu= 0.1$ Pa s as a representative value from this range for comparison with experiments.}
\revise{Figure 4 also shows that the predicted dimensionless wavenumber of dominant mode is very close to unity, and therefore the dimensional wavelength is approximately half channel width ($2\pi H$)}

@@

% Note the spaces between the initials
\bibliography{Grass}{}
\bibliographystyle{jfm}
%\bibliography{Grass}{}
% \bibliographystyle{plain}
%\bibliographystyle{aipauth4-1}
\end{document}

>>>>

\newcommand{\ReyNdg}{{\Rey\Ndg}}
% \newcommand{\revise}[1]{{\color{blue} {#1}}}
\newcommand{\revise}[1]{{{#1}}}

@@

\section{Results - unstable modes and critical parameters}
A threshold in $\Rey$, above which the flow is unstable (Re$(\sigma)>0$) for at least one $k$, emerges from the solution of ~\eqref{Orr-somerfield}. 
The dependence of this threshold $\Rey$, and the corresponding marginally stable wavenumber $k$, on $\delta/H$ and $\hg/H$ is shown in Fig.~\ref{Re_vs_delta}, and is found to compare well with experimental observations of \cite{Ghisal02}.
The threshold $\Rey$ increases with the vegetation density, indicating a competition between the destabilizing shear in the flow, and the stabilizing effect of damping due to vegetation drag.
% A similar conclusion was presented for an analogous problem (flow around an emergent (i.e., $\hg>2H$) sea grass patch), but by assuming $U(y)$ to be a tanh-profile, and neglecting the viscous term \citep{White07}.
%Previous calculations for terrestrial grass either exclude the vegetation drag in their models \cite{Raupach96}, or assume the mean velocity profile \textit{ad hoc} \citep{Raupach96,Delangre06}.
%A threshold flow condition is not reported previously either for terrestrial or submerged marine meadows.
The frequency (Im$(\sigma)$) of the fastest growing mode also agrees well with observed behaviour -- frequency of \monami, maxima in the velocity spectra, and frequency of vortex passage in lab scale experiments \citep{Ghisal02} -- for cases where the vegetation was sufficiently dense to be modeled by a continuum drag field as shown in Fig.~\ref{frequency_comparison}.
\revise{ The measured values of eddy viscosity vary with depth in the water column \citep{Nepf04}; we use $\mu= 0.1$ Pa s as a representative value from this range for comparison with experiments.}
\revise{Figure 2 also shows that the predicted dimensionless wavenumber of the dominant mode for parameters corresponding to the lab scale experiments ($4<H/\delta<10$) is very close to unity, and therefore the dimensional wavelength is approximately $2\pi H$.}

@@

% Note the spaces between the initials
\input{grass.bbl}
% \bibliography{Grass}{}
% \bibliographystyle{jfm}
\end{document}
